### 2021-04-11 submissiondraftIMT.Rmd
Added my submission draft. Ignored pdfs

>>>>

## Predicting Anxiety from COVID Cases Using a Panel Model

We are searching for a way for school administrators to anticipate increased anxiety among their students. In 2020 and today, anecdotally, COVID is a significant source of anxiety. We used a panel model to find the predictiveness of covid cases on anxiety in 18-29 year olds.

Panel models are used for regression when the response and predictor variables are longitudinal. In this case, we treat US states as entities and have longitudinal values for both anxiety and new COVID cases.

For states $s=1,\dots, 50$ and time periods $t=1,\dots,T$, we use the model

$$
\mbox{anx}_{s,t} = \alpha_s + \beta_1 \mbox{anx}_{s,t-1} + \beta_2 \mbox{COVID}_{s,t} + \varepsilon_{s,t}
$$

This model allows for state-specific intercepts ($\alpha_s$), autocorrelation in anxiety within a state ($\beta_1$), and an effect of COVID cases on anxiety ($\beta_1$).

Alternatively, we can have a random effect for the state-specific intercepts,
\begin{align*}
\mbox{anx}_{s,t} &= \alpha + a_s + \beta_1 \mbox{anx}_{s,t-1} + \beta_2 \mbox{COVID}_{s,t} + \varepsilon_{s,t} \\
a_s &\sim N(0, \sigma^2_a)
\end{align*}

The `plm` package in `R` allows us to fit both of these models and perform a hypothesis test to determine which fits our data better.
